---
title: "Final_Project_SP22"
author: "Haoyu Lyu"
date: "4/26/2022"
output: html_document
---

```{r setup, include=FALSE}
# Library the package
library(tidyverse)
library(lubridate)
# Read the data
ratings <- read_csv('ratings.csv')
movies <- read_csv('movies.csv')
tags <- read_csv('tags.csv')
```


### Data Wrangling(1)

```{r message=FALSE,warning=FALSE}
# Set the time format
tags <- tags %>%
  mutate(tag_date = as_datetime(timestamp))
ratings <- ratings %>%
  mutate(rating_date = as_datetime(timestamp))
# show head three row
head(ratings,3)
head(tags,3)
```

### Data wrangling(2)

```{r}
# Join the data tifether and select 7 variables to show as instruction
join <- ratings %>%
  inner_join(tags,by=c('userId','movieId')) %>%
  inner_join(movies,by='movieId') %>%
  select('userId', 'rating', 'rating_date', 'tag', 'tag_date', 'title', 'genres')
# show head three row
head(join,3)
```
Creating a new object called join which shown both rated and tagged movie for further analysis. Put the data together is a way called join.


### Data wrangling(3)

```{r}
# Tidy the data by instruction
Joinnew <- join %>%
  mutate(release_year = str_extract(title,"\\(\\d{4}\\)$")) %>%
  mutate(title = gsub(pattern = "\\(\\d{4}\\)$", replacement = "", title)) %>%
  mutate(release_year = gsub(pattern = "[()]", replacement = "", release_year))
# show head three row
head(Joinnew,3)
```
Create a new data object to separate release year from the title.This object can show release year of each movie to give us furture analysis based on the movie year.






### Data visualization(1)
```{r}
# find the top 10 rated genres
top10genres <- Joinnew %>%
  group_by(genres) %>%
  summarise(count = n()) %>%
  arrange(desc(count))%>%
  head(10)
# using ggplot to show the top 10 rated genres
top10genres %>%
  ggplot(aes(x =reorder(genres,-count), y = count,fill=genres)) +
  geom_bar(stat='identity') +
  ggtitle('Top 10 Rated Movie Genres') +
  xlab('Movie Genres') +
  ylab('Rated Frequency')+
  theme(axis.text.x=element_blank())

```
interpretive statement:
This chart shown the top 10 genres of these movies by decending order should be Drama,Comedy|Crime|Drama|Thriller,Comedy, Drama|Romance,Action|Crime|Drama|Thriller,Comedy|Drama|Romance,Action|Adventure|Sci-Fi, Comedy|Romance,Documentary,Comedy|Drama.Among all of these, Drama almost 30% higher than the second place which is Comedy crime. Drama is the most frequently one. The catagories are very meticulous.












